% -----------------------------------------------------------------------------
% CHAPTER 1: Design objectives and Requirements
% -----------------------------------------------------------------------------
\section{Design objectives and Requirements}
Traffic congestion is a critical issue in many areas. Effective traffic light control is essential for 
managing vehicle flow, reducing bottlenecks, and enhancing road safety. 
This project focuses on simulating a flexible four-way traffic light control 
system that allows for manual intervention and clear status display via an LCD screen.

The main goal is to design and simulate a microcontroller-based traffic light system. 
The system must meet the following technical requirements:
\begin{itemize}
    \vspace{-5pt}
    \item \textbf{Microcontroller:} Utilize a standard 8 - bit microcontroller.
    \vspace{-5pt}
    \item \textbf{Display:} Two sets of traffic lights for two directions. A 16x2 LCD module must display the current mode and the countdown timer.
    \vspace{-5pt}
    \item \textbf{Control Interface:} Four buttons are used to control the system with two modes, each has a distinct set of functionalities.
    \vspace{-5pt}
    In \texttt{AUTO} mode:
    \vspace{-10pt}
    \begin{itemize}
        \item \texttt{MODE} Button: Cycle through operating modes (Automatic $\leftrightarrow$ Manual).
        \item \texttt{CONFIG} Button: Entering configuration mode.
        \item \texttt{UP} Buttons: Increase the Red/Green/Yellow duration.
        \item \texttt{DOWN} Buttons: Decrease the Red/Green/Yellow duration.
    \end{itemize}
    \vspace{-5pt}
    In \texttt{MANUAL} mode:
    \vspace{-10pt}
    \begin{itemize}
        \item \texttt{MODE} Button: Cycle through operating modes (Automatic $\leftrightarrow$ Manual).
        \item \texttt{SWITCH} Button: Changing light signals on each direction.
        \item \texttt{FLASH} Buttons: Flashing Yellow light (Warning signal).
        \item \texttt{RED} Buttons: Red light on both directions (Emergency stop).
    \end{itemize}
    \item \textbf{Safety Logic:} Adherence to traffic regulations must be ensured by satisfying the time constraint:
    \begin{equation}
        T_{Red} = T_{Green} + T_{Yellow}
    \end{equation}
    The system must automatically calculate the Red light duration based on the user-set Green and Yellow times.
\end{itemize}